Notes for the week of 4/27/19 - 5/3/19

### 2019-04-29 notes/weekly_notes/4.27.19.NotesForWeek.tex
added notes made over the weekend

\newcommand{\Csig}{\Cset_{\sigma}}

@@

\title{Notes for the week of 4/8/19 - 4/12/19}
\author{Alden Green}
\date{\today}
\maketitle

Let $\set{x_1, x_2, \ldots}$ be a sequence of points sampled independently from probability measure $\Pbb$ with density function $f$. For each $n$, write $\Xbf_n = \set{x_1, \ldots, x_n} \subseteq \Reals^d$ . Given some $\lambda, \sigma > 0$, let
\begin{equation*}
\mathcal{U} = \set{x: f(x) \geq \lambda},~ \mathcal{C} = \textrm{one connected component of}~ \mathcal{U}, ~\textrm{and}~ \Csig = \Cset + B(0,\sigma)
\end{equation*}

Write $\widetilde{\Xbf}_n = \Csig[\Xbf_n]$, $\widetilde{E}_n = \set{(i,j): x_i, x_j \in \widetilde{\Xbf}_n, \norm{x_i - x_j}_2 \leq r}$ and let $\widetilde{G}_{n,r} = \bigl(\widetilde{\Xbf}_n, \widetilde{E}_n \bigr)$.
For a set $S \subseteq \widetilde{\Xbf}_n$, the normalized cut of $S$ within $\widetilde{G}_{n,r}$ can be defined as
\begin{equation*}
\widetilde{\Phi}_{n,r}(S) := \frac{\widetilde{\cut}(S)}{\min \set{\widetilde{\vol}(S), \widetilde{\vol}(S^c)}},~ \textrm{where}~ \widetilde{\cut}(S) := \cut(S;\widetilde{G}_{n,r}),~ \widetilde{\vol}(S) := \vol(S;\widetilde{G}_{n,r})
\end{equation*}
and in this context $S^c = \widetilde{\Xbf}_n \setminus S$ denotes the complement of $S$ within $\widetilde{G}_{n,r}$. Then, the \emph{graph conductance profile} over $\widetilde{G}_{n,r}$ is
\begin{equation*}
\widetilde{\Phi}_{n,r}(t) := \min_{\substack{S \subseteq \widetilde{\Xbf}_n: \\ 0 < \widetilde{\pi}_n(S) < t} } \widetilde{\Phi}_{n,r}(S)
\end{equation*}
where $\widetilde{\pi}_{n,r}(S) = \frac{\widetilde{\vol}(S)}{\widetilde{\vol}(\widetilde{\Xbf}_n)}$. We will prove a lower bound on the graph conductance profile by a continuous analogue.

\subsection{Continuous conductance}

Let $\nu$ be the Lebesgue measure over Euclidean space $\Rd$, and $B(x,r)$ be a ball of radius $r$ centered at $x$. For $\Sset \subset \Rd$ a Borel set,
\begin{equation*}
\nu_{\Pbb}(\Sset) := \int_{\Sset} f(x) dx
\end{equation*}
is the weighted volume.

The $r$-ball walk over $\Csig$ is a Markov chain, with transition probability given by 
\begin{equation*}
\widetilde{P}_{\Pbb,r}(x; \Sset) := \frac{\nu_{\Pbb}(\Sset \cap B(x,r))}{\nu_{\Pbb}(\Csig \cap B(x,r))} \tag{$x \in \Csig, \Sset \in \mathfrak{B}(\Csig)$}
\end{equation*}
where $\mathfrak{B}(\Csig)$ is the Borel $\sigma$-algebra of $\Csig$.

Denote the stationary distribution for this Markov chain by $\pi_{\Pbb,r}$, which is defined by the relation
\begin{equation*}
\int_{\Csig} \widetilde{P}_{\Pbb,r}(x; \Sset) d\pi_{\Pbb,r}(x) = \pi_{\Pbb,r}(\Sset).  \tag{$\Sset \in \mathfrak{B}(\Csig)$}
\end{equation*}
Letting the \emph{local conductance} be given by
\begin{equation*}
\ell_{\Pbb,r}(x) := \nu_{\Pbb}(\Csig \cap B(x,r)) \tag{$x \in \Csig$}
\end{equation*}
a bit of algebra verifies that
\begin{equation*}
\pi_{\Pbb,r}(\Sset) = \frac{\int_{\Sset} \ell_{\Pbb,r}(x) f(x) dx}{\int_{\Csig} \ell_{\Pbb,r}(x) f(x) dx}. \tag{$\Sset \in \mathfrak{B}(\Csig)$}
\end{equation*}

We next introduce the \emph{ergodic flow}, $\widetilde{Q}_{\Pbb,r}$. Let $\Sset_1 \cap \Sset_2 = \Csig$ be a partition of $\Csig$. Then the ergodic flow between $\Sset_1$ and $\Sset_2$ is given by 
\begin{equation*}
\widetilde{Q}_{\Pbb,r}(\Sset_1, \Sset_2) := \int_{\Sset_1} \widetilde{P}_{\Pbb,r}(x; \Sset_2) d\pi_{\Pbb,r}(x), \tag{$\Sset_1, \Sset_2 \in \mathfrak{B}(\Csig)$}
\end{equation*}
the \emph{(continuous) normalized cut} by
\begin{equation*}
\widetilde{\Phi}_{\Pbb,r}(\Sset) := \frac{\widetilde{Q}_{\Pbb,r}(\Sset_1, \Sset_2)}{\min \set{\pi_{\Pbb,r}(\Sset),\pi_{\Pbb,r}(\Sset^c)}}, \tag{$\Sset \in \mathfrak{B}(\Csig)$}
\end{equation*}
and the \emph{(continuous) conductance profile} by
\begin{equation*}
\widetilde{\Phi}_{\nu,r}(t) := \min_{\substack{\Sset \in \mathfrak{B}(\Csig) \\ 0 < \pi_{\Pbb,r}(\Sset) \leq t} } \widetilde{\Phi}_{\Pbb,r}(\Sset) \tag{$0 < t \leq 1/2 $}
\end{equation*}
where $\Sset^c = \Csig \setminus \Sset$.

To relate the graph and continuous conductance profiles, we introduce mappings between the data $\widetilde{\Xbf}_n$ and the space $\Csig$.

\subsection{Transportation maps and $TL^1$ distance. }
Let
\begin{equation*}
\widetilde{\Pbb}(\Sset) = \frac{\Pbb(\Sset)}{\Pbb(\Csig)}, ~ \widetilde{\Pbb}_{n}(\Sset) := \frac{1}{\widetilde{n}} \sum_{x_i \in \widetilde{\Xbf}_n} \1(x_i \in \Sset) \tag{$\Sset \in \mathfrak{B}(\Csig)$}
\end{equation*} 
be the (empirical) probability measures, conditional on $x \sim \Pbb$ lying within $\Csig$ (Here $\mathfrak{B}(\Csig)$ is the Borel $\sigma$-algebra of $\Csig$). A Borel map $T: \Csig \to \widetilde{\Xbf}_n$ is said to be a \emph{transportation map} between $\widetilde{\Pbb}$ and $\widetilde{\Pbb}_n$ if for arbitrary $\Sset \in \mathfrak{B}(\Csig)$,  
\begin{equation*}
\widetilde{\Pbb}(\Sset) = \widetilde{\Pbb}_n(T(\Sset)).
\end{equation*}

If a sequence of transportation maps $\seq{T_n}$ satisfies $\norm{\mathrm{Id} - T_n}_{L^{1}(\widetilde{\Pbb})} = o_P(1)$, we refer to it as a sequence of \emph{stagnating transportation maps}. Lemma \ref{lem: stagnating_transportation_maps} establishes that with probability one, such a sequence of stagnating transportation maps will exist.
In fact, under suitable conditions, the convergence happens at rate $\left(\frac{\log n}{n}\right)^{1/d}$.

\begin{lemma}[Adaptation of Proposition 5 of \textcolor{red}{Garcia Trillos 2016}]
	\label{lem: stagnating_transportation_maps}
	With probability one, there exists a sequence of transportation maps $\seq{T_n}$, $T_n: \Csig \to \widetilde{\Xbf}_n$ such that the following statement holds:
	\begin{equation*}
	\limsup_{n \to \infty} \frac{\widetilde{n}^{1/d} \norm{\mathrm{Id} - T_n}_{L^{\infty}(\widetilde{\Pbb})}}{(\log \widetilde{n})^{p_d}} \leq C
	\end{equation*}
	where $\mathrm{Id}(x) = x$ is the identity mapping over $\Csig$, $C$ is a universal constant and $p_d = 3/4$ for $d = 2$ and $1/d$ for $d \geq 3$.
\end{lemma}

\begin{definition}
	For a sequence $\seq{u_n} \subseteq L^1(\widetilde{\Pbb}_n)$ and $u \in L^1(\widetilde{\Pbb})$, we say that $\seq{u_n}$ converges $TL^1$ to $u$ if there exists a sequence of stagnating transportation maps $\seq{T_n}$ such that
	\begin{equation}
	\label{eqn: transportation_distance_1}
	d^{TL^1}(u,u_n) := \int_{\Csig} \abs{u(x) - u_n \circ T_n(x)} d \widetilde{\Pbb}(x) \overset{n}{\to} 0 
	\end{equation}
	and denote it $u_n \overset{TL^1}{\to} u$.
\end{definition}

\begin{remark}
	\label{rmk: transportation_distance_equivalence}
	Note that as written this is not a metric, as $u$ and $u_n$ lie in different spaces. Technically, we can resolve this by writing
	\begin{equation}
	\label{eqn: transportation_distance_2}
	d^{TL^1}((\widetilde{\Pbb}, u),(\widetilde{\Pbb}_n,u_n)) = \inf_{\pi \in \Gamma(\widetilde{\Pbb},\widetilde{\Pbb}_n)} \iint_{\Csig \times \Csig} \abs{x - y} + \abs{f(x) - g(y)} d\pi(x,y)
	\end{equation}
	where $\gamma$ is the space of couplings over the measures $\widetilde{\Pbb}, \widetilde{\Pbb}_n$. However, it can be shown that \eqref{eqn: transportation_distance_2} converges to zero if and only if \eqref{eqn: transportation_distance_1} is satisfied and 
	\begin{equation*}
	\widetilde{\Pbb}_n \overset{w}{\to} \widetilde{\Pbb}.
	\end{equation*}

	Since this additional condition will be satisfied with probability one, we simplify things by hereafter referring only to the condition in \eqref{eqn: transportation_distance_1}. See \textcolor{red}{Garcia Trillos 15} for more details.
\end{remark}

\section{Lower bound graph conductance profile}

In order to lower bound the graph conductance profile $\widetilde{\Phi}_{n,r}(\cdot)$, we will need to split the analysis into two cases based on the size of $S \subseteq \widetilde{\Xbf}_n$. Define the \emph{graph local spread} to be
\begin{equation*}
s(G) := \frac{9}{10} \min_{u \in V} \set{\mathrm{deg}(u;G)} \cdot \min_{u \in V} \set{\pi(u;G)}.  \tag{$G = (V,E)$}
\end{equation*}

Theorem \ref{thm: graph_conductance_profile_lb_1} states that for subsets of $\widetilde{\Xbf}_n$ with volume at least $s(G)$, the graph normalized cut can be uniformly lower bounded by the continuous normalized cut. Sections \ref{sec: proof_and_supporting_theory} and \ref{sec: other_results} contains the proof of Theorem \ref{thm: graph_conductance_profile_lb_1} along with other relevant results.

\begin{theorem}
	\label{thm: graph_conductance_profile_lb_1}
	Let $\Csig$ satisfy Assumption \ref{asmp: embedding} with respect to Lipschitz constant $L$ and convex set $K$ with diameter $D_K$. Then,
	\begin{equation*}
	\liminf_{n \to \infty} \Bigl\{ \min_{S \in \mathcal{L}(\widetilde{G}_{n,r})} \widetilde{\Phi}_{n,r}(S) \Bigr\} \geq \frac{\lambda_{\sigma}^4 r}{\Lambda_{\sigma}^4 2^{12} D_K L \sqrt{d}}
	\end{equation*}
	where $\mathcal{L}(\widetilde{G}_{n,r}) = \set{S \subseteq \widetilde{\Xbf}_n: \widetilde{\pi}_{n,r}(S) \geq s(\widetilde{G}_{n,r})}$
\end{theorem}

Lemma \ref{lem: graph_conductance_profile_lb_1} shows that for the remaining small sets, the graph normalized cut is of constant order. 
\begin{lemma}
	\label{lem: graph_conductance_profile_lb_1}
	Let $G = (V,E)$ be an undirected graph, and $\mathcal{L}(G) = \set{S \subseteq V: \pi(S; G) \geq s(G)}$. Then,
	\begin{equation*}
	\min_{S \not\in \mathcal{L}(G)}\Phi(S; G) \geq \frac{1}{10}.
	\end{equation*}
\end{lemma}
\begin{proof}
	Clearly, for any $u \in S$
	\begin{equation}
	\label{eqn: graph_conductance_profile_lb_1}
	\cut(\set{u}, S^c; G) \geq \deg(u;G) - \abs{S}
	\end{equation}

	Then, since $\pi(S;G) \leq s(G)$,
	\begin{equation*}
	\abs{S} \leq \pi(S;G) \cdot \frac{\vol(V;G)}{\min_{u \in V} \set{\mathrm{deg}(u;G)}} = \frac{\pi(S;G)}{\min_{u \in V} \set{\pi(u;G)}} \leq \frac{9}{10} \min_{u \in V} \set{\mathrm{deg}(u;G)},
	\end{equation*}
	and therefore by \eqref{eqn: graph_conductance_profile_lb_1}, for any $u \in S$
	\begin{equation*}
	\cut(\set{u}, S^c; G) \geq \deg(u;G) - \frac{9}{10} \min_{u \in V} \set{\mathrm{deg}(u;G)} \geq \frac{1}{10}\deg(u;G)
	\end{equation*}
	and the statement follows by summing over all $u \in S$. 
\end{proof}

Theorem \ref{thm: graph_conductance_profile_lb_1} and Lemma \ref{lem: graph_conductance_profile_lb_1} together yield Corollary \ref{cor: graph_conductance_profile_lb}, the main result of these notes.

\begin{corollary}[Lower bound on graph conductance profile]
	\label{cor: graph_conductance_profile_lb}
	Let $\Csig$ satisfy Assumption \ref{asmp: embedding} with respect to Lipschitz constant $L$ and convex set $K$ with diameter $D_K$. Then, with probability one the following asymptotic lower bound holds on the graph conductance function
	\begin{equation*}
	\liminf_{n \to \infty} \widetilde{\Phi}_{n,r}(t) \geq \min\set{\frac{\lambda_{\sigma}^4 r}{\Lambda_{\sigma}^4 2^{12} D_K L \sqrt{d}}, \frac{1}{10}} \tag{$0 \leq t \leq \frac{1}{2}$}
	\end{equation*}
\end{corollary}

\section{Proofs and Supporting Theory}
\label{sec: proof_and_supporting_theory}

\subsection{Proof of Theorem \ref{thm: graph_conductance_profile_lb_1}.}

By Lemma \ref{lem: stagnating_transportation_maps}, with probability one there exists a sequence of stagnating transportation maps from $\widetilde{\Pbb}$ to $\widetilde{\Pbb}_n$, which we will denote $\seq{T_n}$.

For $S \subseteq \widetilde{\Xbf}_n$, let $T_n^{-1}(S) = \set{x \in \Csig: T_n(x) \in S}$ be the preimage of $T_n$, and note that $T_n^{-1}(S^c) = \Csig \setminus T_n^{-1}(S)$.

Letting
\begin{equation*}
\xi_n := \frac{\int_{\Csig} \ell_{\Pbb,r_n^-}(x) f(x) dx}{\int_{\Csig} \ell_{\Pbb,r_n^+}(x) f(x) dx},~ \gamma_n(S) := \frac{\min \set{\pi_{\Pbb,r_n^-}(T_n^{-1}(S^c)), \pi_{\Pbb,r_n^-}(T_n^{-1}(S^c))} }{\min \set{\pi_{\Pbb,r_n^+}(T_n^{-1}(S^c)), \pi_{\Pbb,r_n^+}(T_n^{-1}(S^c))} } 
\end{equation*}
where $r_n^{\pm} := r \pm \norm{\mathrm{Id} - T_n}_{L^{\infty}(\widetilde{\Pbb})}$, by Lemma \ref{lem: graph_to_continuous_conductance} and Corollary \ref{cor: nonuniform_continuous_conductance} we have that for all $S \subseteq \widetilde{\Xbf}_n$,
\begin{align}
\widetilde{\Phi}_{n,r}(S) & \geq \xi_n \gamma_n(S) \widetilde{\Phi}_{\Pbb,r_n^{-}}(T_n^{-1}(S)) \nonumber \\
& \geq  \xi_n \gamma_n(S) \frac{\lambda_{\sigma}^4r_n^{-}}{2^{12} \Lambda_{\sigma}^4 D_K L \sqrt{d}}. \label{eqn: graph_ncut_lb_1}
\end{align}

By Lemma \ref{lem: cont_local_conductance}, with probability one
\begin{equation*}
\liminf_{n \to \infty} \xi_n = 1.
\end{equation*}

By Lemma \ref{lem: stationary_dist_lb}, letting $c$ be any constant satisfying $c > \frac{9\lambda_{\sigma}^4 \nu_d r^d}{50\Lambda_{\sigma}^2}$, there exists some $n \in \Naturals$ such that for all $S \in \mathcal{L}(\widetilde{G}_{n,r})$,
\begin{equation*}
\pi_{\Pbb,r}(T_n^{-1}(S)) \geq c > 0
\end{equation*}
and therefore by Lemma \ref{lem: cont_stationary_dist}
\begin{equation*}
\liminf_{n \to \infty} \biggl\{ \inf_{S \in \mathcal{L}(\widetilde{G}_{n,r})} \gamma_n(S)\biggr\} = 1.
\end{equation*}

As Lemma \ref{lem: stagnating_transportation_maps} implies $r_n^{-} \to r$ with probability one, an application of Slutsky's Theorem to \eqref{eqn: graph_ncut_lb_1} completes the proof.

\subsection{Graph functionals to continuous functionals.}

Lemmas \ref{lem: volume_bound} and \ref{lem: cut_bound} provide the necessary bounds for the $\cut$ and $\vol$ functionals in terms of continuous analogues.

\begin{lemma}
	\label{lem: volume_bound}
	Let $S \subseteq \widetilde{\Xbf}_n$, and let $T_n$ be a transportation map between $\widetilde{\Pbb}$ and $\widetilde{\Pbb}_n$. Then, letting $\Sset = \set{x \in \Csig: T_n(x) \in S}$
	\begin{equation*}
	\frac{1}{\widetilde{n}^2}\widetilde{\vol}(S) \leq \frac{\int_{\Csig} \ell_{\Pbb,r_n^+}(x) f(x) dx}{\Pbb(\Csig)^2} \pi_{\Pbb,r_n^+}(\Sset)
	\end{equation*}
	where $r_n^+ = r + \norm{\mathrm{Id} - T_n}_{L^{\infty}(\widetilde{\Pbb})}$. 
\end{lemma}
\begin{proof}
	Let $u: \widetilde{\Xbf}_n \to \set{0,1}$ be the characteristic function for $S$, meaning
	\begin{equation*}
	u(x) = 
	\begin{cases}
	1,~ x \in S \\
	0,~ \text{otherwise}
	\end{cases}
	\end{equation*}

	Now, we proceed
	\begin{align}
	\frac{1}{\widetilde{n}^2} \widetilde{\vol}(S_n) & = \frac{1}{\widetilde{n}^2} \sum_{x_i, x_j \in \widetilde{\Xbf}_n} \1(\norm{x_i - x_j} \leq r) \abs{u(x_i)} \nonumber \\
	& = \iint_{\Csig \times \Csig} \1(\norm{x - y} \leq r) \abs{u(x)} d\widetilde{\Pbb}_n(x) d\widetilde{\Pbb}_n(y) \nonumber \\
	& =  \iint_{\Csig \times \Csig} \1(\norm{T_n(x) - T_n(y)} \leq r) \abs{u \circ T_n(x)} d\widetilde{\Pbb}(x) d\widetilde{\Pbb}(y) \nonumber \\
	& \leq \iint_{\Csig \times \Csig} \1(\norm{x - y} \leq r_n^+) \abs{u \circ T_n(x)} d\widetilde{\Pbb}(x) d\widetilde{\Pbb}(y) \label{eqn: vol_ub}\\
	& = \int_{\Sset} \int_{\Csig \cap B(x,r_n^+)} 1 d\widetilde{\Pbb}(y) d\widetilde{\Pbb}(x) \nonumber
	\end{align}

	By definition we have $\frac{d\widetilde{\Pbb}(x)}{d\Pbb(x)} = \Pbb(\Csig)$. Therefore,
	\begin{align*}
	\int_{\Sset} \int_{\Csig \cap B(x,r_n^+)} 1 d\widetilde{\Pbb}(y) d\widetilde{\Pbb}(x) & = \frac{1}{\Pbb(\Csig)^2}\int_{\Sset} \int_{\Csig \cap B(x,r_n^+)} 1 d\Pbb(y) d\Pbb(x) \\
	& = \frac{1}{\Pbb(\Csig)^2}\int_{\Sset} \ell_{\Pbb,r_n^+}(x) f(x) dx \\
	& = \frac{\int_{\Csig} \ell_{\Pbb,r}(x) f(x) dx}{\Pbb(\Csig)^2} \pi_{\Pbb,r_n^+}(\Sset)
	\end{align*}
	which is the desired upper bound. The lower bound follows a similar proof, with the only change being \eqref{eqn: vol_ub}, where $r_n^+$ is replaced by $r_n^-$ and the inequality is reversed.
\end{proof}

\begin{lemma}
	\label{lem: cut_bound}
	Let $S \subseteq \widetilde{\Xbf}_n$, and let $T_n$ be a transportation map between $\widetilde{\Pbb}$ and $\widetilde{\Pbb}_n$. Then, letting $\Sset = \set{x \in \Csig: T_n(x) \in S}$,
	\begin{equation*}
	\frac{1}{\widetilde{n}^2} \widetilde{\cut}(S) \geq \frac{\int_{\Csig} \ell_{\Pbb,r_n^-}f(x) dx}{\Pbb(\Csig)^2} \widetilde{Q}_{\Pbb,r_n^-}(\Sset, \Sset^c) 
	\end{equation*}
	where $r_n^- = r - \norm{\mathrm{Id} - T_n}_{L^\infty(\widetilde{\Pbb})}$
\end{lemma}
\begin{proof}
	Let $u: \widetilde{\Xbf}_n \to \set{0,1}$ be the characteristic function for $S$, meaning
	\begin{equation*}
	u(x) = 
	\begin{cases}
	1,~ x \in S \\
	0,~ \text{otherwise}
	\end{cases}
	\end{equation*}

	We proceed according to a very similar set of steps as Lemma \ref{lem: volume_bound}:
	\begin{align*}
	\frac{1}{\widetilde{n}^2} \widetilde{\cut}(S) & = \frac{1}{\widetilde{n}^2} \sum_{x_i, x_j \in \widetilde{\Xbf}_n} \1(\norm{x_i - x_j} \leq r) \abs{u(x_i) - u(x_j)} \\
	& = \iint_{\Csig \times \Csig} \1(\norm{x - y} \leq r) \abs{u(x) - u(y)} d\widetilde{\Pbb}_n(x) d\widetilde{\Pbb}_n(y) \\
	& =  \iint_{\Csig \times \Csig} \1(\norm{T_n(x) - T_n(y)} \leq r) \abs{u \circ T_n(x) - u \circ T_n(y)} d\widetilde{\Pbb}(x) d\widetilde{\Pbb}(y) \\
	& \geq \iint_{\Csig \times \Csig} \1(\norm{x - y} \leq r_n^-) \abs{u \circ T_n(x) - u \circ T_n(y)} d\widetilde{\Pbb}(x) d\widetilde{\Pbb}(y) \\
	& = \int_{\Sset} \int_{\Sset^c \cap B(x,r_n^-)} d\widetilde{\Pbb}(y) d\widetilde{\Pbb}(x)
	\end{align*}
	We conclude similarly to the proof of Lemma \ref{lem: volume_bound},
	\begin{align*}
	\int_{\Sset} \int_{\Sset^c \cap B(x,r_n^-)} d\widetilde{\Pbb}(y) d\widetilde{\Pbb}(x) & = \frac{1}{\Pbb(\Csig)^2} \int_{\Sset} \int_{\Sset^c \cap B(x,r_n^-)} d\Pbb(y) d\Pbb(x) \\
	& = \frac{\int_{\Csig} \ell_{\Pbb,r_n^-}f(x) dx}{\Pbb(\Csig)^2} \widetilde{Q}_{\Pbb,r_n^-}(\Sset, \Sset^c).
	\end{align*}	
\end{proof}

\begin{lemma}
	\label{lem: graph_to_continuous_conductance}
	Let $\seq{T_n}$ be a sequence of transportation maps from $\widetilde{\Pbb}$ to $\widetilde{\Pbb}_n$, and let
	\begin{equation*}
	r_n^- = r - \norm{\mathrm{Id} - T_n}_{L^{\infty}(\widetilde{\Pbb})},~ r_n^+ = r + \norm{\mathrm{Id} - T_n}_{L^{\infty}(\widetilde{\Pbb})}.
	\end{equation*}

	Fix $S \subseteq \widetilde{\Xbf}_n$. Then, letting $\Sset = \set{x \in \Csig: T_n(x) \in S}$,
	\begin{equation}
	\label{eqn: graph_to_continuous_conductance}
	\widetilde{\Phi}_{n,r}(S) \geq \frac{\int_{\Csig} \ell_{\Pbb,r_n^-}(x) f(x) dx}{\int_{\Csig} \ell_{\Pbb,r_n^+}(x) f(x) dx}  \frac{\min \set{\pi_{\Pbb,r_n^-}(\Sset), \pi_{\Pbb,r_n^-}(\Sset^c)} }{\min \set{\pi_{\Pbb,r_n^+}(\Sset), \pi_{\Pbb,r_n^+}(\Sset^c)} } \widetilde{\Phi}_{\Pbb,r_n^{-}}(\Sset)
	\end{equation}
\end{lemma}
\begin{proof}

	By Lemmas \ref{lem: volume_bound} and \ref{lem: cut_bound},
	\begin{equation*}
	\frac{\widetilde{\cut}(S)}{\widetilde{\vol}(S)} \geq \frac{\int_{\Csig} \ell_{\Pbb,r_n^-}(x) f(x) dx}{\int_{\Csig} \ell_{\Pbb,r_n^+}(x) f(x) dx} \frac{\widetilde{Q}_{\Pbb,r_n^-}(\Sset, \Sset^c)}{\pi_{\Pbb,r_n^+}(\Sset)}
	\end{equation*}

	But, noting that $\Sset^c = \set{x \in \Csig: T_n(x) \in S^c}$, Lemmas \ref{lem: volume_bound} and \ref{lem: cut_bound} also imply
	\begin{equation*}
	\frac{\widetilde{\cut}(S^c)}{\widetilde{\vol}(S^c)} \geq \frac{\int_{\Csig} \ell_{\Pbb,r_n^-}(x) f(x) dx}{\int_{\Csig} \ell_{\Pbb,r_n^+}(x) f(x) dx} \frac{\widetilde{Q}_{\Pbb,r_n^-}(\Sset^c, \Sset)}{\pi_{\Pbb,r_n^+}(\Sset^c)}
	\end{equation*}
	and as $\widetilde{Q}_{\Pbb,r_n^-}(\cdot, \cdot)$ is symmetric in its arguments we obtain
	\begin{equation*}
	\frac{\widetilde{\cut}(S)}{\min\set{\widetilde{\vol}(S), \widetilde{\vol}(S^c)}} \geq \frac{\int_{\Csig} \ell_{\Pbb,r_n^-}(x) f(x) dx}{\int_{\Csig} \ell_{\Pbb,r_n^+}(x) f(x) dx} \frac{\widetilde{Q}_{\Pbb,r_n^-}(\Sset, \Sset^c)}{\min \set{\pi_{\Pbb,r_n^+}(\Sset), \pi_{\Pbb,r_n^+}(\Sset^c)} },
	\end{equation*}
	and the proof is complete.
\end{proof}

\subsection{Perturbation asymptotics.}

>>>>

\newcommand{\Csig}{\Cset_{\sigma}}
\newcommand{\Asig}{\Aset_{\sigma}}

@@

\title{Notes for the week of 4/27/19 - 5/3/19}
\author{Alden Green}
\date{\today}
\maketitle

Let $\Aset \subseteq \Reals^d$, and for $\sigma \geq 0$, write $\sigma B := B(0,\sigma) = \set{x \in \Rd: \norm{x} \leq \sigma}$ for the closed ball of radius $\sigma$ centered at the origin (and let $B^{\circ}(0,\sigma)$ denote the corresponding open ball). Let $\Asig = \Aset + \sigma B$ be the direct sum of $\Aset$ and $\sigma B$.

\begin{theorem}
	\label{thm: expansion_volume}
	If $\Aset$ is closed and bounded, then for any $\delta > 0$,
	\begin{equation*}
	\nu(\Asig + \delta B) \leq \left(1 + \frac{\delta}{\sigma}\right)^d \nu(\Asig).
	\end{equation*}
\end{theorem}
\begin{proof}
	We will show that for any $\epsilon > 0$, 
	\begin{equation}
	\label{eqn: ratio_of_volume}
	\frac{\nu(\Asig + \delta B)}{\nu(\Asig)} \leq \frac{(\sigma + \delta + \epsilon)^d}{\sigma^d}
	\end{equation}
	which is sufficient to prove the claim.

	Fix $\epsilon > 0$. Our first goal is to find a finite collection $x_1, \ldots, x_N \in \Rd$ such that
	\begin{equation*}
	\bigcup_{i = 1}^{N} B(x_i, \sigma) \subseteq \Asig \subset \bigcup_{i = 1}^{N} B(x_i, \sigma + \epsilon). \tag{$N := N(\epsilon)$}
	\end{equation*}

	Observe that since $\Aset$ is closed and bounded, it is compact. As $B(x,\sigma)$ is compact, and the direct sum of two compact sets is also compact, $\Asig$ is compact. Moreover,
	\begin{equation*}
	\Asig \subset \bigcup_{x \in \Aset} B^{\circ}(x,\sigma + \epsilon)
	\end{equation*}
	so by compactness there exists $x_1, \ldots,x_N \in \Aset$ such that
	\begin{equation*}
	\Asig \subset \bigcup_{i = 1}^{N} B^{\circ}(x_i,\sigma + \epsilon).
	\end{equation*}

	By the triangle inequality, $\Asig + \delta B \subset \bigcup_{i = 1}^{N} B^{\circ}(x_i,\sigma + \epsilon + \delta)$. Of course, for each $x_i \in \Aset$, $B(x_i,\sigma) \in \Asig$. Summarizing our findings, we have
	\begin{equation}
	\label{eqn: finite_subcover}
	\bigcup_{i = 1}^{N} B(x_i,\sigma) \subseteq \Asig  ,~\Asig + \delta B \subset \bigcup_{i = 1}^{N} B^{\circ}(x_i,\sigma + \delta + \epsilon)
	\end{equation}

	We proceed by giving a lower bound on $\nu(\Asig)$. Partition $\Asig$ using the balls $B(x_i,\sigma)$, meaning let $\Aset_{\sigma}^{(1)} := B(x_1,\sigma)$, $\Aset_{\sigma}^{(2)} := B(x_2,\sigma) \setminus B(x_1,\sigma)$, and continuing, so that
	\begin{equation*}
	\Aset_{\sigma}^{(i)} := B(x_i,\sigma) \setminus \bigcup_{j = 1}^{i - 1} \Aset_{\sigma}^{(j)}. \tag{$i = 1,\ldots,N$}
	\end{equation*}
	Of course, by \eqref{eqn: finite_subcover} $\Asig \supseteq \bigcup_{i = 1}^{N} \Asig^{(i)}$. Therefore,
	\begin{align*}
	\nu(\Asig) & \geq \sum_{i = 1}^{N} \nu(\Asig^{(i)}) \\
	& = \sigma^d \nu_d \sum_{i = 1}^{N}  \frac{\nu(\Asig^{(i)})}{\nu(B(x_i,\sigma))} \\
	& =: \sigma^d \nu_d \sum_{i = 1}^{N} c_i.
	\end{align*}

	Now we turn to proving an upper bound on $\nu(\Asig + \delta B)$. Let $\Aset_{\sigma + \epsilon + \delta}^{(1)} := B(x_1,\sigma + \delta + \epsilon)$ and
	\begin{equation*}
	\Aset_{\sigma + \delta + \epsilon}^{(i)} := B(x_i,\sigma + \delta + \epsilon) \setminus \bigcup_{j = 1}^{i - 1} \Aset_{\sigma + \delta + \epsilon}^{(j)}. \tag{$i = 1,\ldots,N$}
	\end{equation*}

	By \eqref{eqn: finite_subcover},
	\begin{equation*}
	\Aset_{\sigma} + \delta B \subset \bigcup_{i =1}^{N} \Aset_{\sigma + \delta + \epsilon}^{(i)}
	\end{equation*}
	and as a result
	\begin{align*}
	\nu(\Aset_{\sigma + \delta}) & \leq \sum_{i = 1}^{N} \Aset_{\sigma + \delta + \epsilon}^{(i)} \\
	& = \sum_{i = 1}^{N} \nu_d (\sigma + \delta + \epsilon)^d \frac{\nu(\Aset_{\sigma + \delta + \epsilon}^{(i)})}{\nu(B(x_i, \sigma + \delta + \epsilon))} \\
	& \leq \nu_d (\sigma + \delta + \epsilon)^d \sum_{i = 1}^{N} c_i
	\end{align*}
	where the last inequality follows from Lemma \ref{lem: covering}. We have shown \eqref{eqn: ratio_of_volume}, and thus the claim.
\end{proof}

\section{Additional Theory}

\begin{lemma}
	\label{lem: covering}
	For $i = 1, \ldots, N$ and  $A_{\sigma}^{(i)}, A_{\sigma + \delta + \epsilon}^{(i)}$ as in Theorem \ref{thm: expansion_volume},
	\begin{equation*}
	\frac{\nu(\Aset_{\sigma + \delta + \epsilon}^{(i)})}{\nu(B(x_i, \sigma + \delta + \epsilon))} \leq \frac{\nu(\Aset_{\sigma}^{(i)})}{\nu(B(x_i, \sigma))}
	\end{equation*}
\end{lemma}
\begin{proof}
	Let $\delta' := \delta + \epsilon$. It will be sufficient to show that
	\begin{equation*}
	\biggl(\Aset_{\sigma + \delta'}^{(i)} - \set{x_i}\biggr) \subseteq \left(1 + \frac{\delta'}{\sigma}\right)\cdot\biggl(\Asig^{(i)} - \set{x_i}\biggr) 
	\end{equation*}
	since then
	\begin{equation*}
	\nu(\Aset_{\sigma + \delta'}^{(i)}) \leq \left(1 + \frac{\delta'}{\sigma}\right)^d \nu(\Aset_{\sigma}) = \frac{\nu(B(x_i, \sigma + \delta'))}{\nu(B(x_i, \sigma))} \nu(\Aset_{\sigma}).
	\end{equation*}

	Assume without loss of generality that $x_i = 0$, and let $x \in \Aset_{\sigma + \delta'}^{(i)}$, meaning
	\begin{equation}
	\norm{x} \leq \sigma + \delta',~ \norm{x - x_j} > \sigma + \delta'~ \textrm{for $j = 1, \ldots, i - 1$}.
	\end{equation}
	Letting $x' = \frac{\sigma}{\sigma + \delta'} x$, since $\norm{x} \leq \sigma + \delta'$, $\norm{x'} \leq \sigma$ and therefore $x' \in B(0,\sigma)$. Additionally observe that for any $j = 1, \ldots, i - 1$, by the triangle inequality
	\begin{equation*}
	\norm{x' - x_j} \geq \norm{x - x_j} - \norm{x - x'} > \sigma + \delta' - \frac{\delta'}{\sigma + \delta'}\norm{x} \geq \sigma
	\end{equation*}
	and therefore $x' \not\in B(x_j,\sigma)$ for any $j = 1,\ldots, i - 1$. So $x' \in \Asig^{(i)}$.
\end{proof}
